---
title: "Springer Nature survey analysis"
author: "Rick Gilmore"
date: "`r Sys.Date()`"
bibliography: refs.bib
output: 
  html_document:
    code_folding: hide
params:
  download_datafile: false
  data_destfile: "data/survey.xlsx"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

This document summarizes the results of a survey completed by Springer Nature in 2018.

The survey results are discussed in [[@Stuart_undated-tw]](https://doi.org/10.6084/m9.figshare.5975011) and the raw data are found in [[@Astell2018-sc]](https://doi.org/10.6084/m9.figshare.5971387.v1).

## Setup

Ensure that we have the required package dependencies in the local environment.

```{r}
require(readxl)
require(tidyverse)
library(tidyverse) # for pipe %>% operator
```

## Import

The data are in figshare.
Here is the download link from the API: <https://figshare.com/ndownloader/files/10968194>
The data file is an Excel spreadsheet in the .xlsx format.

By default, we do _not_ download the datafile each time we run this report.
Set `params$download_datafile` to `true` in the YAML header or run `rmarkdown::render("index.Rmd", params=list(download_datafile=TRUE))` to download the datafile.

```{r}
if (params$download_datafile) {
  message("Downloading datafile")
  download.file(url = "https://figshare.com/ndownloader/files/10968194", destfile = params$data_destfile)
} else {
  message("Using locally stored file: ", params$data_destfile)
  if (!file.exists(params$data_destfile)) {
    stop("Local data file not found: ", params$data_destfile)
  }
}
```

```{r}
survey <- readxl::read_xlsx("data/survey.xlsx")
```

Examine the structure of the imported file.

```{r}
str(survey)
```

There are `r dim(survey)[1]` responses and `r dim(survey)[2]` questions.

Here are the questions:

```{r}
names(survey)
```

## Clean

## Visualize

## References