---
title: "Springer Nature survey analysis"
author: "Rick Gilmore"
date: "`r Sys.Date()`"
bibliography: include/refs.bib
css: include/styles.css
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
params:
  download_datafile: false
  data_destfile: "data/survey.xlsx"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

This document summarizes the results of a survey completed by Springer Nature in 2018.

The survey results are discussed in [[@Stuart_undated-tw]](https://doi.org/10.6084/m9.figshare.5975011) and the raw data are found in [[@Astell2018-sc]](https://doi.org/10.6084/m9.figshare.5971387.v1).

## Setup

Ensure that we have the required package dependencies in the local environment.

```{r}
require(readxl)
library(tidyverse) # for pipe %>% operator
library(targets)
```

## Import

The data are in figshare.
Here is the download link from the figshare API: <https://figshare.com/ndownloader/files/10968194>.
The data file is an Excel spreadsheet in the .xlsx format.

By default, we do _not_ download the datafile each time we run this report.
Set `params$download_datafile` to `true` in the YAML header or run `rmarkdown::render("index.Rmd", params=list(download_datafile=TRUE))` to download the datafile.

```{r}
if (params$download_datafile) {
  message("Downloading datafile")
  download.file(url = "https://figshare.com/ndownloader/files/10968194", destfile = params$data_destfile)
} else {
  message("Using locally stored file: ", params$data_destfile)
  if (!file.exists(params$data_destfile)) {
    stop("Local data file not found: ", params$data_destfile)
  }
}
```

```{r}
survey <- readxl::read_xlsx("data/survey.xlsx")
```

Examine the structure of the imported file.

```{r}
str(survey)
```

There are `r dim(survey)[1]` responses and `r dim(survey)[2]` questions.

Here are the questions:

```{r}
names(survey)
```

## Clean

### "`r names(survey)[1]`"

Rename.

```{r}
names(survey)[1] <- "job_title"
```

Examine (unique) values.

```{r}
length(unique(survey$job_title))
```

That field will require a lot of consolidation and cleaning.
We'll skip it for now.

### "`r names(survey)[2]`"

Rename (to lowercase).

```{r}
names(survey)[2] <- tolower(names(survey)[2])
```

Examine (unique) values.

```{r}
length(unique(survey$country))
```

So, there was a broad international set of respondents.
We'll just show the top of the list.

```{r}
by_country <- survey %>%
  dplyr::group_by(., country) %>%
  dplyr::summarise(., n_resp = n()) %>%
  dplyr::arrange(., desc(n_resp))

head(by_country) %>%
  knitr::kable(., format = 'html') %>%
  kableExtra::kable_classic(.)
```

### "`r names(survey)[3]`"

Rename.

```{r}
names(survey)[3] <- "what_do_with_data"
```

Examine unique responses.

```{r}
length(unique(survey$what_do_with_data))
```

```{r}
unique(survey$what_do_with_data)
```

These values could be simplified and made lowercase.

```{r}
survey <- survey %>%
  dplyr::mutate(
    .,
    what_do_with_data = dplyr::recode(what_do_with_data, "Submit files as supplementary information" = "submit_suppl")
  ) %>%
  dplyr::mutate(
    .,
    what_do_with_data = dplyr::recode(what_do_with_data, "Deposit files in a repository" = "deposit_repo")
  ) %>%
  dplyr::mutate(., what_do_with_data = tolower(what_do_with_data))
```

```{r}
xtabs(formula = ~ what_do_with_data, data = survey)
```

### "`r names(survey)[4]`"

Rename.

```{r}
names(survey)[4] <- "generate_human_data"
```

Examine unique values.

```{r}
unique(survey$generate_human_data)
```

Recode the 0, 1 values as `FALSE`, `TRUE`.

```{r}
survey <- survey %>%
  dplyr::mutate(., generate_human_data = as.logical(generate_human_data))
```

```{r}
xtabs(formula = ~ generate_human_data, data = survey)
```

### "`r names(survey)[5]`"

Rename.

```{r}
names(survey)[5] <- "file_size"
```

Examine unique values.

```{r}
unique(survey$file_size)
```

There are a small number of unique values and these have a logical ordering.

```{r}
ordered_file_sz <- forcats::fct_relevel(survey$file_size, c("<20Mb", "20Mb -100Mb", "100Mb - 1Gb", "1Gb - 5Gb", "5Gb - 20Gb", "20Gb - 50 Gb", ">50Gb"))

survey <- survey %>%
  dplyr::mutate(., file_size = ordered_file_sz)
```

Summarize.

```{r}
xtabs(formula = ~ file_size, data = survey)
```

### "`r names(survey)[6]`"

Rename.

```{r}
names(survey)[6] <- "subject_area"
```

Recode.

```{r}
survey <- survey %>%
  dplyr::mutate(., subject_area = tolower(subject_area)) %>%
  dplyr::mutate(., subject_area = stringr::str_replace(subject_area, " ", "_"))
```

Summarize.

```{r}
xtabs(formula = ~ subject_area, data = survey)
```

### "`r names(survey)[7]`"

Rename.

```{r}
names(survey)[7] <- "molecular_or_gene_data"
```

Examine unique values

```{r}
unique(survey$molecular_or_gene_data)
```

Recode the 0, 1 values as `FALSE`, `TRUE`.

```{r}
survey <- survey %>%
  dplyr::mutate(., molecular_or_gene_data = as.logical(molecular_or_gene_data))
```

Summarize.

```{r}
xtabs(formula = ~ molecular_or_gene_data, data = survey)
```

### "`r names(survey)[8]`"

Rename.

```{r}
names(survey)[8] <- "deposit_repo_always"
```

Examine unique values.

```{r}
unique(survey$deposit_repo_always)
```

Recode the 0, 1 values as `FALSE`, `TRUE`.

```{r}
survey <- survey %>%
  dplyr::mutate(., deposit_repo_always = as.logical(deposit_repo_always))
```

Summarize.

```{r}
xtabs(formula = ~ deposit_repo_always, data = survey)
```

### "`r names(survey)[9]`"

Rename.

```{r}
names(survey)[9] <- "aware_should_deposit"
```

Examine unique values.

```{r}
unique(survey$aware_should_deposit)
```

Recode the 0, 1 values as `FALSE`, `TRUE`.

```{r}
survey <- survey %>%
  dplyr::mutate(., aware_should_deposit = as.logical(aware_should_deposit))
```

Summarize.

```{r}
xtabs(formula = ~ aware_should_deposit, data = survey)
```

### "`r names(survey)[10]`"

Rename.

```{r}
names(survey)[10] <- "generate_other_types"
```

Examine unique values.

```{r}
unique(survey$generate_other_types)
```

Recode the 0, 1 values as `FALSE`, `TRUE`.

```{r}
survey <- survey %>%
  dplyr::mutate(., generate_other_types = as.logical(generate_other_types))
```

Summarize.

```{r}
xtabs(formula = ~ aware_should_deposit, data = survey)
```

### "`r names(survey)[11]`"

Rename.

```{r}
names(survey)[11] <- "data_discoverable_importance"
```

Examine unique values.

```{r}
unique(survey$data_discoverable_importance)
```

This looks like a numeric score in the range of [0,10].

```{r}
survey %>%
  ggplot(.) +
  aes(x = data_discoverable_importance) +
  geom_bar()
```

### Questions about "barriers"

It looks like questions 12 to 17 relate to barriers.
[**Check the report to confirm this**]{.blue}.
We can proceed with cleaning without confirming.

```{r}
names(survey)[12] <- "barrier_lack_of_time"
names(survey)[13] <- "barrier_organizing_data"
names(survey)[14] <- "barrier_which_repo"
names(survey)[15] <- "barrier_copyright_licensing"
names(survey)[16] <- "barrier_sharing_cost"
names(survey)[17] <- "barrier_other"
```

Recode values (except for `barrier_other`) as Booleans.

```{r}
# This is not elegant, but it is clear
lack_time <- stringr::str_detect(survey$barrier_lack_of_time, "Lack")
org_data <- stringr::str_detect(survey$barrier_organizing_data, "Organising")
dont_know_repo <- stringr::str_detect(survey$barrier_which_repo, "repository")
copyright <- stringr::str_detect(survey$barrier_copyright_licensing, "copyright")
costs <- stringr::str_detect(survey$barrier_sharing_cost, "Costs")

survey <- survey %>%
  dplyr::mutate(., barrier_lack_of_time = if_else(lack_time, TRUE, FALSE, missing = FALSE),
                barrier_organizing_data = if_else(org_data, TRUE, FALSE, missing = FALSE),
                barrier_which_repo = if_else(dont_know_repo, TRUE, FALSE, missing = FALSE),
                barrier_copyright_licensing = if_else(copyright, TRUE, FALSE, missing = FALSE),
                barrier_sharing_cost = if_else(costs, TRUE, FALSE, missing = FALSE))
```

```{r}
xtabs(formula = ~ barrier_lack_of_time, data = survey)
```

```{r}
xtabs(formula = ~ barrier_organizing_data, data = survey)
```

```{r}
xtabs(formula = ~ barrier_which_repo, data = survey)
```

```{r}
xtabs(formula = ~ barrier_copyright_licensing, data = survey)
```

```{r}
xtabs(formula = ~ barrier_sharing_cost, data = survey)
```

The `barrier_other` category is a free-response field.
Here is a sample of the responses:

```{r}
head(unique(survey$barrier_other))
```

### "`r names(survey)[18]`"

Rename.

```{r}
names(survey)[18] <- "interest_data_dep_service"
```

Examine unique values.

```{r}
unique(survey[,18])
```

This looks like a numeric scale in [0,10].

```{r}
survey %>%
  ggplot(.) +
  aes(x = interest_data_dep_service) +
  geom_bar()
```

### "`r names(survey)[19]`"

Rename.

```{r}
names(survey)[19] <- "interest_data_discov_service"
```

Examine unique values.

```{r}
unique(survey[,19])
```

This is also a numeric scale.

```{r}
survey %>%
  ggplot(.) +
  aes(x = interest_data_discov_service) +
  geom_bar()
```

### "`r names(survey)[20]`"

Rename.

```{r}
names(survey)[20] <- "have_data_to_deposit"
```

Examine unique values.

```{r}
unique(survey$have_data_to_deposit)
```

Recode this as a logical value.

```{r}
survey <- survey %>%
  dplyr::mutate(., have_data_to_deposit = as.logical(have_data_to_deposit))
```

Summarize.

```{r}
xtabs(formula = ~ have_data_to_deposit, data = survey)
```

### "`r names(survey)[21]`"

Rename.

```{r}
names(survey)[21] <- "want_other_help"
```

Examine unique values.

```{r}
unique(survey$want_other_help)
```

Recode this as a logical value.

```{r}
survey <- survey %>%
  dplyr::mutate(., want_other_help = as.logical(want_other_help))
```

Summarize.

```{r}
xtabs(formula = ~ want_other_help, data = survey)
```

### "`r names(survey)[22]`"

Rename.

```{r}
names(survey)[22] <- "want_help_with"
```

This is a free response field, so here are some examples:

```{r}
head(unique(survey$want_help_with))
```

### "`r names(survey)[23]`"

Rename.

```{r}
names(survey)[23] <- "have_addtl_info"
```

Recode this as a logical value.

```{r}
survey <- survey %>%
  dplyr::mutate(., have_addtl_info = as.logical(have_addtl_info))
```

Summarize.

```{r}
xtabs(formula = ~ have_addtl_info, data = survey)
```

### "`r names(survey)[24]`"

Rename.

```{r}
names(survey)[24] <- "addtl_info"
```

This is a free reponse field, so here are some examples.

```{r}
head(unique(survey$addtl_info))
```

## Save cleaned

```{r}
readr::write_csv(survey, "data/survey_clean.csv")
message("Saved cleaned data file: ", "data/survey_clean.csv")
```

## Cross-tabs

### Importance that data is discoverable by field

```{r}
survey %>%
  ggplot(.) +
  aes(x = data_discoverable_importance, fill = subject_area) +
  geom_bar()
```

### Interest in data deposit service by field

```{r}
survey %>%
  ggplot(.) +
  aes(x = interest_data_dep_service, fill = subject_area) +
  geom_bar()
```

### Interest in data deposit service for those who do or do not generate data from human participants

```{r}
survey %>%
  ggplot(.) +
  aes(x = interest_data_dep_service, fill = generate_human_data) +
  geom_bar()
```


### Interest in data discoverability service by field

```{r}
survey %>%
  ggplot(.) +
  aes(x = interest_data_discov_service, fill = subject_area) +
  geom_bar()
```

### Prevalence of barriers to better data practices by subject area

```{r}
xtabs(formula = ~ subject_area + barrier_lack_of_time, data = survey)
```

```{r}
xtabs(formula = ~ subject_area + barrier_organizing_data, data = survey)
```

```{r}
xtabs(formula = ~ subject_area + barrier_which_repo, data = survey)
```

```{r}
xtabs(formula = ~ subject_area + barrier_copyright_licensing, data = survey)
```

```{r}
xtabs(formula = ~ subject_area + barrier_sharing_cost, data = survey)
```

## References