---
title: "Springer Nature survey report"
author: "Rick Gilmore"
date: "`r Sys.Date()`"
bibliography: include/refs.bib
css: include/styles.css
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(tidyverse))
```

## Purpose

This document summarizes the results of a survey completed by Springer Nature in 2018.

The survey results are discussed in [[@Stuart_undated-tw]](https://doi.org/10.6084/m9.figshare.5975011) and the raw data are found in [[@Astell2018-sc]](https://doi.org/10.6084/m9.figshare.5971387.v1).

## Download

The data are in figshare.
Here is the download link from the figshare API: <https://figshare.com/ndownloader/files/10968194>.
The data file is an Excel spreadsheet in the .xlsx format.

## Import and clean

Functions to import the downloaded XLSX file from `data/survey.xlsx` are in `R/functions.R`.

## Re-import cleaned

```{r}
ns_survey <- readr::read_csv("data/survey_clean.csv", show_col_types = FALSE)
head(ns_survey)
```

## Visualize

### N responses by country

There were responses from $n=$ `r length(unique(ns_survey$country))` unique countries.

```{r}
ns_survey %>%
  dplyr::group_by(., country) %>%
  dplyr::summarise(., n_resp_from_country = n()) %>%
  dplyr::arrange(., desc(n_resp_from_country)) %>%
  ggplot2::ggplot() +
  ggplot2::aes(x = n_resp_from_country) +
  ggplot2::geom_histogram(bins = 100)
```

Countries with more than 100 respondents include the following:

```{r}
top_repondents <- ns_survey %>%
  dplyr::group_by(., country) %>%
  dplyr::summarise(., n_resp_from_country = n()) %>%
  dplyr::filter(., n_resp_from_country >= 100) %>%
  dplyr::arrange(., desc(n_resp_from_country)) %>%
  dplyr::ungroup(.)

top_repondents %>%
  knitr::kable(., format = 'html') %>%
  kableExtra::kable_classic(.)  
```

### N responses by subject area

```{r}
ns_survey |>
  xtabs(formula = ~ subject_area)
```
```{r}
ns_survey %>%
  dplyr::filter(., !is.na(subject_area)) %>%
  ggplot() +
  aes(subject_area, fill = subject_area) +
  geom_bar() +
  ylab("N repondents")
```

## Cross-tabs

### Importance that data are discoverable by field

```{r}
ns_survey %>%
  filter(., !is.na(data_discoverable_import), 
         !is.na(subject_area)) %>%
  ggplot() +
  aes(x = data_discoverable_import, fill = subject_area) +
  facet_grid(rows = vars(subject_area)) +
  scale_x_continuous(breaks = 0:10) +
  geom_bar()
```

```{r}
mod_discoverable <- lm(formula = data_discoverable_import ~ subject_area, ns_survey)
anova(mod_discoverable)
summary(mod_discoverable)
```

### Interest in data deposit service by field

```{r}
ns_survey %>%
  filter(., !is.na(interest_data_dep_service), 
         !is.na(subject_area)) %>%
  ggplot(.) +
  aes(x = interest_data_dep_service, fill = subject_area) +
  facet_grid(rows = vars(subject_area)) +
  scale_x_continuous(breaks = 0:10) +
  geom_bar()
```

```{r}
mod_interest_data_serv <- lm(formula = interest_data_dep_service ~ subject_area, ns_survey)
anova(mod_interest_data_serv)
summary(mod_interest_data_serv)
```

### Interest in data deposit service for those who do or do not generate data from human participants

```{r}
ns_survey %>%
  dplyr::filter(., !is.na(interest_data_dep_service),
                !is.na(generate_human_data)) %>%
  ggplot(.) +
  aes(x = interest_data_dep_service, fill = generate_human_data) +
  geom_bar()
```

```{r}
mod_interest_data_serv_human_data <- lm(formula = interest_data_dep_service ~ generate_human_data, ns_survey)
anova(mod_interest_data_serv_human_data)
summary(mod_interest_data_serv_human_data)
```

### Interest in data discoverability service by field

```{r}
ns_survey %>%
  dplyr::filter(., !is.na(interest_data_discov_service),
                !is.na(subject_area)) %>%
  ggplot(.) +
  aes(x = interest_data_discov_service, fill = subject_area) +
  geom_bar()
```

### Prevalence of barriers to better data practices by subject area

```{r}
ns_survey |> xtabs(formula = ~ subject_area + barrier_lack_of_time)

barriers <- ns_survey %>%
  dplyr::filter(., !is.na(subject_area)) %>%
  tidyr::pivot_longer(., cols = c(12:16), names_to = "sharing_barriers", values_to = "sharing_barriers_vals", values_drop_na = TRUE) 

barriers %>%
  ggplot() +
  aes(x = sharing_barriers, y = as.numeric(sharing_barriers_vals), fill = sharing_barriers) +
  geom_col() +
  ylab("N responses") +
  coord_flip() +
  facet_wrap(~subject_area) +
  theme(legend.position = "none") 

```

## References

